An eight-year-long low-frequency earthquake catalog for Southern Cascadia

### 2022-03-21 paper/agujournaltemplate_highlighted.tex
Submit second revision

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={7.5cm 1cm 28cm 2cm},clip]{figures/hist.eps}
\caption{Cross-correlation values for LFEs added in the catalog for family E (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right). There were no missing LFEs for this family.}
\label{pngfiguresample}
\end{figure}

@@

We note that there is a good spatial and temporal agreement between tremor and LFEs, with LFEs detected during the main tremor episodes. Additional small LFE episodes are also detected between bigger tremor episodes. The LFE families located south on the strike-slip fault from the San Andreas Fault system have much shorter recurrence intervals than the LFE families located on the subduction zone. Additionally, one LFE family located on the southern end of the subduction zone (family A at 40.09N and 34.9km depth) has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families. \\

@@

\section{Results}

@@

where $\Delta \tau$ is the change in shear stress on the fault plane in the slip direction, $\Delta \sigma$ is the change in fault normal stress (positive is tensile), $\mu$ is the coefficient of intrinsic friction, $\Delta \sigma_m$ is the change in mean stress and $B$ is the Skempton's coefficient ~\cite{HOU_2015}. We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient, as was done by ~\citeA{HOU_2015}. We then divided the values of tidal Coulomb stress change into 20 stress bins and computed for each LFE family the number of LFEs occurring at a time when the value of the stress was in a given bin. We also computed what would be the expected number of LFEs occurring if the tidal stress changes have no influence on LFE activity. As noted by ~\citeA{HOU_2015}, tremor sensitivity to stress perturbations changes during an ETS event, with an increase in sensitivity to tidal stress as slip accumulates over several days. We thus choose to only consider the later part of the 2008 ETS event, using only LFEs that occurred between 1.5 and 11.5 days after the arrival of the tremor front. As there are only a few LFEs \textbf{in many of the families}, the influence of tidal stress on LFE activity \textbf{is not always clear}. However, Figure 10 shows the number of LFEs occurring during each stress bin (blue bars) and the expected number of LFEs (black line) for six families with a relatively high number of LFEs. For most of the families, a positive Coulomb stress change (promoting shear failure) is associated with an increase in LFE activity \textbf{, as is the case in northern Cascadia ~\cite{HOU_2015}}. However, this is not the case for the southernmost LFE family A, for which a negative Coulomb stress change is associated with an increase in LFE activity. To better highlight the behavior of family A, we also consider the whole LFE catalog and plot the observed and expected number of LFEs as a function of tidal stress. We clearly see that these LFEs tend to occur during times when predicted tidal Coulomb stress is discouraging slip on the plate boundary. We tried to relocate this LFE family using new templates obtained from LFEs present in both the 2007-2009 FAME catalog and the 2004-2011 networks catalog. We locate the family using S minus P times for each station, or using P-P times between \textbf{pairs of} stations, or using a combination of both. The family may be located 30 to 50 kilometers east from the initial location given by ~\citeA{PLO_2015}. The depth is 20-25 kilometers, that is shallower than the location given by ~\citeA{PLO_2015} and shallower than the plate boundary. However, this does not change the pattern observed for the correlation between tidal stress changes and LFE activity. We hypothesize that LFE family A may not be located on the subduction zone and may be on a nearby crustal fault. If this was the case, the fault plane assumed for the tidal stress calculation would not be appropriate, which \textbf{could} explain the different pattern for this LFE family. The LFE families located on the San Andreas fault by ~\citeA{SHE_2017} have a depth of 15 to 30 kilometers, so the depth of the LFE family A is compatible with a location on a crustal fault.

>>>>

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 25.5cm 0cm},clip]{figures/hist.eps}
\caption{Cross-correlation values for LFEs added in the catalog for family E (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right). There were no missing LFEs for this family.}
\label{pngfiguresample}
\end{figure}

@@

We note that there is a good spatial and temporal agreement between tremor and LFEs, with LFEs detected during the main tremor episodes. Additional small LFE episodes are also detected between bigger tremor episodes. The LFE families located south on the strike-slip fault from the San Andreas Fault system have much shorter recurrence intervals than the LFE families located on the subduction zone. Additionally, one LFE family located on the southern end of the subduction zone (family A at 40.09N and 34.9km depth) \textbf{also has} shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families. \\

@@

%\section{Results}

@@

where $\Delta \tau$ is the change in shear stress on the fault plane in the slip direction, $\Delta \sigma$ is the change in fault normal stress (positive is tensile), $\mu$ is the coefficient of intrinsic friction, $\Delta \sigma_m$ is the change in mean stress and $B$ is the Skempton's coefficient ~\cite{HOU_2015}. We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient, as was done by ~\citeA{HOU_2015}. We then divided the values of tidal Coulomb stress change into 20 stress bins and computed for each LFE family the number of LFEs occurring at a time when the value of the stress was in a given bin. We also computed what would be the expected number of LFEs occurring if the tidal stress changes have no influence on LFE activity. As noted by ~\citeA{HOU_2015}, tremor sensitivity to stress perturbations changes during an ETS event, with an increase in sensitivity to tidal stress as slip accumulates over several days. We thus choose to only consider the later part of the 2008 ETS event, using only LFEs that occurred between 1.5 and 11.5 days after the arrival of the tremor front. As there are only a few LFEs \textbf{in many of the families}, the influence of tidal stress on LFE activity \textbf{is not always clear}. However, Figure 10 shows the number of LFEs occurring during each stress bin (blue bars) and the expected number of LFEs (black line) for six families with a relatively high number of LFEs. For most of the families, a positive Coulomb stress change (promoting shear failure) is associated with an increase in LFE activity \textbf{, as is the case in northern Cascadia ~\cite{HOU_2015}}. \\

However, this is not the case for the southernmost LFE family A, for which a negative Coulomb stress change is associated with an increase in LFE activity. To better highlight the behavior of family A, we also consider the whole LFE catalog and plot the observed and expected number of LFEs as a function of tidal stress. We clearly see that these LFEs tend to occur during times when predicted tidal Coulomb stress is discouraging slip on the plate boundary. We tried to relocate this LFE family using new templates obtained from LFEs present in both the 2007-2009 FAME catalog and the 2004-2011 networks catalog. We locate the family using S minus P times for each station, or using P-P times between \textbf{pairs of} stations, or using a combination of both. The family may be located 30 to 50 kilometers east from the initial location given by ~\citeA{PLO_2015}. The depth is 20-25 kilometers, that is shallower than the location given by ~\citeA{PLO_2015} and shallower than the plate boundary. However, this does not change the pattern observed for the correlation between tidal stress changes and LFE activity. We hypothesize that LFE family A may not be located on the subduction zone and may be on a nearby crustal fault. If this was the case, the fault plane assumed for the tidal stress calculation would not be appropriate, which \textbf{could} explain the different pattern for this LFE family. The LFE families located on the San Andreas fault by ~\citeA{SHE_2017} have a depth of 15 to 30 kilometers, so the depth of the LFE family A is compatible with a location on a crustal fault.
